\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

%During my time working on Belle~II the BEAST~II, I did several tasks. In the interest of making my contribution to the project clear, I thought I would mention here what I have done. 

I worked on Belle~II and BEAST~II for five years. The following summarizes my contributions to the project.

For the entirety of my time on Belle~II, I was the electromagnetic calorimeter (ECL) representative to the beam background simulation group. This involved determining the expected dose and neutron flux in the electromagnetic calorimeter ECL using Strategic Accelerator Design (SAD) and GEometry ANd Tracking (GEANT4) simulations of the beam backgrounds produced by the beam background simulation group leader, Hiro Nakayama. A new background simulation was produced three times a year, requiring new plots of the effect on the ECL. It was through these studies that it was determined that a method of verifying the simulation was needed, particularly for neutrons.

I joined the BEAST~II group to develop a thermal neutron detector system for the Belle~II commissioning. My research determined that tubes of \he were the best method. I contacted GE/Reuter-Stokes to purchase these. Neil Honkanen from the University of Victoria's (UVIC) electronics shop designed readout electronics for the \he tubes and I tested them with the thermal neutron source at UVIC. With the assistance of Paul Poffenberger and Peter Lewis, I developed data acquisition software to record the data produced by the tubes. I had the tubes shipped to KEK in August 2015 and travelled to KEK myself to install them. I travelled to KEK in February 2016 for the start of commissioning, and again in May 2016 for the BEAST~II machine studies. I completed the calibration when the \he tubes were shipped back to UVIC in September 2016.  

The simulation of BEAST~II Phase~I was performed by Igal Jaegle. With advice from him and others in the BEAST~II group, I re-scaled these simulations to match the beam conditions observed in Phase~I with advice from Igal. With assistance from my supervisor Michael Roney, I developed the simulation re-weighting scheme described in Chapter \ref{chap:Sim}, and the analysis techniques discussed in Chapter \ref{chap:Anal}.

A Nuclear Instruments and Methods article is in preparation on BEAST~II Phase~I, which will describe this and other BEAST~II work.

